A large-scale analysis of racial disparities in police stops across the

### 2019-07-29 lib/paper_results.Rmd
Update to match paper text

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>% 
  group_by(subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

>>>>

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```
